Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny1
small changes

We have revised the manuscript ``Hydrodynamics of a semipermeable inextensible membrane under flow and confinement"  
by Bryan Quaife, Ashley Gannon and Y.-N. Young, 
based on 
the referees' very helpful feedback.  
Thanks to the referees' comments
and suggestions, we believe the revised manuscript is much
improved. 
In the revised manuscript we ensure that
all of their concerns and questions are properly addressed.
Below is a summary of the revisions made in the new manuscript.
The detailed {\bf Response:}s to comments of referees are listed in 
{\bf Response:} to Referee 1 and Referee 2.
We hope that the referees and the
editor will now find the paper suitable for publication in 
Physical Review Fluids.

\vspace{0.5cm}
{\large \bf List of changes}
In the following we refer to 
Referee 1 who has four comments and Referee 2 who has a list of comments. In the revised manuscript the modifications in the text are in blue.

@@

@@

\begin{enumerate}
\item {\bf 
The referee wrote:
``It is stated in the introduction that stretching (due to poration…)
give rise to enhanced membrane permeability to both water and
macromolecules such as ATP. Regarding ATP this is possible. In normal
conditions ATP is released thanks to protein change of conformation
that open channels and I am not sure the evoked permeability is a
similar phenomenon. A few words of clarification are needed."}

@@

We agree with the referee that the ATP release is mostly understood when it is through the coupling between Px1 (activated by membrane tension) and CFTR (activated by membrane deformation), and it is not well understood yet how ATP can be released by diffusing through the membrane. We have thus modified this sentence to avoid confusion.

\noindent
{\bf Location:}  The second paragraph of Introduction, five lines above Figure 1: ``....reaches the order of 2-4 mN/m, giving rise to
membrane rupture and leakage of macromolecules (see Razizadeh {\it et al. }$^{20}$ and references therein)."

@@

\noindent
{\bf Response:}: We thank the referee for this point. In our formulation, the permeation flux is proportional to the hydrostatic pressure and the normal component of the membrane force, which is the capillary pressure due to the Lagrange multiplier tension. The tangential force component due to tension field does not contribute to the permeation flux. To elucidate the relative contribution between the hydrostatic pressure and the normal component of the membrane force, we have conducted computations 
added a short paragraph to illustrate how the relative contributions are in all cases.

@@

\noindent
{\bf Response:}: We have mislabeled the $Ca_E$ in figure 5:  $Ca_E=10^0$ for the solid curves and the $Ca_E=10$ for the dashed curves. To address the effect of Capillary number on the relaxation of a semipermeable vesicle, we have continued the simulations for the cases of $Ca_E = 10$ much further to better illustrate the evolution of reduced area towards equilibrium.

@@

\noindent
{\bf Response:}: The shapes along the blue curve in Figure 7(b) are equilibrium shapes that enclose a constant area but with an efflux (blue) and an influx (red) that adds to zero. Inset c illustrates the evolution from initial  the configuration (I) to the equilibrium (shape III), which corresponds to the case with the largest displacement on the blue curve. To better present all these results, we have taken out the insets (c) and (d) and moved them to the new Figure 7 (a) and (b). The new Figure 7 (c) and (d) are the old Figure  7 (a) and (b).

@@

For the closely-fit channel the imposed flow at the inlet/outlet is set $U_{max}=1000$ $\mu$m/s to match the experimental conditions. As a result the membrane tension is dominant over membrane bending in their contribution to the permeating flux. For the contracting channel, the imposed flow at the inlet/outlet is smaller and yet the strong confinement still gives rise to a membrane tension that dominates in contributing to the permeating flux. We also added new paragraphs to discuss these new results.

@@

\noindent
{\bf Response:}: The referee is correct that numerical simulations of two-dimensional fluid flow could be ideal and the connection to the real experiments is qualitative at best. The studies of two-dimensional vesicle hydrodynamics, however, have shown that the connection to real experiments or 3d simulations could be more than purely qualitative. For example, for a vesicle in a planar shear flow, the transition from tank-treading to tumbling is predicted in both 2 and 3-dimensions, at similar viscosity contrast. Ghiliotti, Biben and Misbah (JFM, 2010) showed that results for a two-dimensional vesicle could be corrected systematically to agree with the three-dimensional results. More recently, the two-dimensional results in Zhang, Shen, Hogan, Barakat and Misbah are also in more than qualitative agreement with real experiments (Biophys. J, 2018).

@@

\item {\bf The referee wrote: ``On the last page: “We observe lose of”è“We observe loss of”."}

\noindent
{\bf Response:}: \end{enumerate}

>>>>

We have revised the manuscript ``Hydrodynamics of a semipermeable inextensible membrane under flow and confinement"  
by Bryan Quaife, Ashley Gannon, and Y.-N. Young, 
based on 
the referees' very helpful feedback.  
Thanks to the referees' comments
and suggestions, we believe the revised manuscript is much
improved. 
In the revised manuscript we ensure that
all of their concerns and questions are properly addressed.
Below is a summary of the revisions made in the new manuscript.
The detailed {\bf Response:}s to comments of referees are listed in 
{\bf Response:} to Referee 1 and Referee 2.
We hope that the referees and the
editor will now find the paper suitable for publication in 
Physical Review Fluids.

\vspace{0.5cm}
{\large \bf List of changes}
In the following we refer to Referee 1 who has five comments and Referee
2 who has three comments. In the revised manuscript the modifications in
the text are in blue.

@@

We thank the referee for their assessment of our work. The following is
our response to each of the specific comments and suggestions.

@@

\begin{enumerate}
\item {\bf 
The referee wrote:
``It is stated in the introduction that stretching (due to
    poration...) give rise to enhanced membrane permeability to
    both water and macromolecules such as ATP. Regarding ATP this is
    possible. In normal conditions ATP is released thanks to protein
    change of conformation that open channels and I am not sure the
    evoked permeability is a similar phenomenon. A few words of
    clarification are needed."}

@@

We agree with the referee that the ATP release is mostly understood when
    it is through the coupling between Px1 (activated by membrane
    tension) and CFTR (activated by membrane deformation), and it is not
    yet well-understood how ATP can be released by diffusing through the
    membrane. We have thus modified this sentence to avoid confusion.

\noindent
{\bf Location:}  The second paragraph of the Introduction, five lines
    above Figure 1: ``....reaches the order of 2-4 mN/m, giving rise to
    membrane rupture and leakage of macromolecules (see Razizadeh {\it
    et al. }$^{20}$ and references therein)."

@@

\noindent
{\bf Response:}: We thank the referee for this point. In our
    formulation, the permeation flux is proportional to the hydrostatic
    pressure and the normal component of the membrane force, which is
    the capillary pressure due to the Lagrange multiplier tension. The
    tangential force component due to tension field does not contribute
    to the permeation flux. To elucidate the relative contribution
    between the hydrostatic pressure and the normal component of the
    membrane force, we have conducted computations and added a short
    paragraph to illustrate the relative contributions in all cases.

@@

\noindent
{\bf Response:}: We have mislabeled the $Ca_E$ in Figure 5:  $Ca_E=10^0$
for the solid curves and the $Ca_E=10$ for the dashed curves. To address
the effect of Capillary number on the relaxation of a semipermeable
vesicle, we have continued the simulations for the cases of $Ca_E = 10$
much further to better illustrate the evolution of reduced area towards
equilibrium.

@@

\noindent
{\bf Response:}: The shapes along the blue curve in Figure 7(b) are
equilibrium shapes that enclose a constant area but with an efflux
(blue) and an influx (red) that adds to zero. Inset (c) illustrates the
evolution from initial  the configuration (I) to the equilibrium (shape
III), which corresponds to the case with the largest displacement on the
blue curve. To better present all these results, we have taken out the
insets (c) and (d) and moved them to the new Figure 7(a) and (b). The
new Figure 7(c) and (d) are the old Figure 7(a) and (b).

@@

For the closely-fit channel the imposed flow at the inlet/outlet is
$U_{max}=1000$ $\mu$m/s to match the experimental conditions. As a
result the membrane tension is dominant over membrane bending in their
contribution to the permeating flux. For the contracting channel, the
imposed flow at the inlet/outlet is smaller and yet the strong
confinement still gives rise to a membrane tension that dominates in
contributing to the permeating flux. We also added new paragraphs to
discuss these new results.

@@

\noindent
{\bf Response:}: The referee is correct that numerical simulations of
    two-dimensional fluid flow could be ideal and the connection to the
    real experiments is qualitative at best. The studies of
    two-dimensional vesicle hydrodynamics, however, have shown that the
    connection to real experiments or 3D simulations could be more than
    purely qualitative. For example, for a vesicle in a planar shear
    flow, the transition from tank-treading to tumbling is predicted in
    both 2- and 3-dimensions, at similar viscosity contrast. Ghiliotti,
    Biben, and Misbah (JFM, 2010) showed that results for a
    two-dimensional vesicle could be corrected systematically to agree
    with the three-dimensional results. More recently, the
    two-dimensional results in Zhang, Shen, Hogan, Barakat, and Misbah
    are also in more than qualitative agreement with real experiments
    (Biophys.~J, 2018).

@@

\item {\bf The referee wrote: ``On the last page: ``We observe lose
  of"$\rightarrow$``We observe loss of"."}

\noindent
{\bf Response:}: Thank you for catching this error. It has been
corrected.
